---
title: "Automatic Phylogenetic Tree Generator"
author: "Christophe Benjamin"
date: "May 6th 2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aptg}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Use of aptg

The aptg package is used to generate phylogenetic trees from a vector of species names or a tree of a taxon down to whatever taxon that is included in the first one. The phylogenetic tree are generated from brranching::phylomatic based on the program of the same name accessible there : http://phylodiversity.net/phylomatic/. 

When the tree is generated from a vector of species names, distance matrices are given. 

##taxa.tree

```{r include=FALSE}
library(aptg)

```

The function needs a vector or list of strings of species name as an input and will give phylogenetic trees and distance matrices as an output. Let's do an example with a mixed list of mammal and angiosperm species. 

```{r taxa.tree, echo=TRUE, message=FALSE, results="hide"}
taxa.tree(species = c("Canis lupus", "Canis latrans", "Acer saccharum", "Castor canadensis", "Alces alces", "Acer rubrum", "Vulpes vulpes", "Salix babylonica", "Odocoileus virginianus", "Betula alleghaniensis", "Rangifer tarandus","Juniperus occidentalis"))
```

As you can see the taxa have been sorted by reference trees; mammals and angiosperms.  The distance matrices are also an output (not shown here). 

## downto.tree
This function creates a phylogenetic tree from a taxon down to another one. For now, only the input species gives a result, but any higher taxon can be choosed. 

```{r downto.tree, echo=-1,message=FALSE, results='hide', fig.height=6, fig.width=6}
Sys.setenv(ENTREZ_KEY="2a3e497f3b180829c87cafafac7a122d9f09") #API key for NCBI
downto.tree("Cervidae", "species")
```

